Election Security with Risk-Limiting Audits

### 2022-04-12 MultipleRoundSims/poster.tex
notes

\BRAVO requires the smallest expected number of ballots when ballots are drawn one at a time and the (true) underlying election is as announced. 
In real audits, election officials draw ballots in rounds because their is some overhead with each round (e.g. opening ballot boxes).
Therefore a more sophisticated workload model has a per ballot cost $c_b$ and a per round cost $c_r$. 
Let $n$ be the number of ballots sampled and $j$ be the number of rounds. Then the cost $C$ is given by 
$$C(n,j) = c_b\cdot n + c_r\cdot j,$$
and depending on the ratio between $c_b$ and $c_r$, we should expect that certain round schedules
achieve lower expected cost.

@@

\begin{itemize}
\item
The efficiency of \Minerva is great, but it lacks the flexibility of \BRAVO in choosing round sizes based on previous samples.
\item
\Prov is our novel RLA which has the efficiency of \Minerva and the flexibility of \BRAVO.
\item For alternative hypothesis $H_a$ that the election is truly as announced and null
hypothesis $H_0$ that the true election is a tie, \BRAVO has the stopping condition that
for $k$ cumulative ballots for the winner and $n$ cumulative sampled ballots,
$$\sigma(k,n,p_a,p_0) \triangleq \frac{\Pr[K=k\mid H_a]}{\Pr[K=k\mid H_0]}\ge \frac{1}{\alpha}.$$
\item \Minerva has the stopping condition that in round $j$ with cumulative winner ballots $k_j$ and round sizes $n_1,n_2,\ldots,n_j$
$$\tau_j(k_j,n_1,n_2,\ldots,n_j,p_a,p_0) \triangleq \frac{\Pr[K_j\ge k_j \wedge \mathcal{A}_{i<j}(X)\neq Correct \mid H_a]}{\Pr[K_j\ge k_j \wedge \mathcal{A}_{i<j}(X)\neq Correct \mid H_0]}\ge \frac{1}{\alpha}.$$ Testing this stopping condition requires computationaly expensive convolutions.
\item The \Prov stopping condition uses ideas from both \BRAVO and \Minerva and requires no convolution to test:
$$\omega_j(k_{j-1},k_j,n_{j-1},n_j,p_a,p_0)\triangleq \sigma(k_{j-1},n_{j-1},p_a,p_0)\cdot \tau_1(k_j,n_j,p_a,p_0) \ge \frac{1}{\alpha}.$$

@@

\heading {Resistance against an adversary} 
If adversary $\mathcal{A}$ has knowledge of previous samples and chooses round size $n_j$ in round $j$, 
\Prov is still risk-limiting.

@@

Need to fill in simulation results here. I am thinking (a) risk simulations as evidence that \Prov is an RLA, 
and (b) number of ballot results if I get them done quickly enough.

@@

    %\nocite{*}
    \footnotesize{\bibliographystyle{plain}\bibliography{audits}}
    %\bibliographystyle{splncs04}
    %\bibliography{audits}

>>>>

\emph{I initially wrote this section since I'd really like to have some evidence that for certain workload parameters, we see an optimal
number of rounds greater than 1 with Providence. I am working on that code now.}

\BRAVO requires the smallest expected number of ballots when ballots are drawn one at a time and the (true) underlying election is as announced. 
In real audits, election officials draw ballots in rounds because their is some overhead with each round (e.g. opening ballot boxes).
Therefore a more sophisticated workload model has a per ballot cost $c_b$ and a per round cost $c_r$. 
Let $n$ be the number of ballots sampled and $j$ be the number of rounds. Then the cost $C$ is given by 
$$C(n,j) = c_b\cdot n + c_r\cdot j,$$
and depending on the ratio between $c_b$ and $c_r$, we should expect that certain round schedules
achieve lower expected cost.
\end{block}

@@

\begin{itemize}
\item
The efficiency of \Minerva is great, but it lacks the flexibility of \BRAVO in choosing round sizes based on previous samples.
\item
\Prov is our novel RLA which has the efficiency of \Minerva and the flexibility of \BRAVO.
\item For alternative hypothesis $H_a$ that the election is truly as announced and null
hypothesis $H_0$ that the true election is a tie, \BRAVO has the stopping condition that
for $k$ cumulative ballots for the winner and $n$ cumulative sampled ballots,
$$\sigma(k,n,p_a,p_0) \triangleq \frac{\Pr[K=k\mid H_a, n]}{\Pr[K=k\mid H_0, n]}\ge \frac{1}{\alpha}.$$
\item \Minerva has the stopping condition that in round $j$ with cumulative winner ballots $k_j$ and round sizes $\bar n_j = n_1,n_2,\ldots,n_j$
$$\tau_j(k_j,\bar n_j,p_a,p_0) \triangleq \frac{\Pr[K_j\ge k_j \wedge \mathcal{A}_{i<j}(X)\neq Correct \mid H_a, \bar n_j]}{\Pr[K_j\ge k_j \wedge \mathcal{A}_{i<j}(X)\neq Correct \mid H_0, \bar n_j]}\ge \frac{1}{\alpha}.$$ Testing this stopping condition requires computationaly expensive convolutions.
\item The \Prov stopping condition uses ideas from both \BRAVO and \Minerva and requires no convolution to test:
$$\omega_j(k_{j-1},k_j,n_{j-1},n_j,p_a,p_0)\triangleq \sigma(k_{j-1},n_{j-1},p_a,p_0)\cdot \tau_1(k_j,n_j,p_a,p_0) \ge \frac{1}{\alpha}.$$

@@

\heading {Resistance against an adversary} 
If adversary $\mathcal{A}$ has knowledge of previous samples and chooses round size $n_j$ in round $j$, 
\Prov is still risk-limiting. Proof of this and the RLA property of \Prov are currently being revised for submission.

@@

\emph{Need to fill in simulation results here. I am thinking (a) risk simulations as evidence that \Prov is an RLA, and (b) number of ballot results if I get them done quickly enough.}

Simulations are currently running to explore the risk, stopping probability, and number of ballots used by \Prov.

@@

    %\nocite{*}
    %\footnotesize{\bibliographystyle{plain}\bibliography{audits}}
    \bibliographystyle{splncs04}
    %\bibliographystyle{plain}
    \bibliography{audits}
    \emph{Having some latex trouble here, but should include r2b2, the recent simulations paper, bravo paper, athena paper, ...}
